Analysis of `mycAffyData` from Loven et al. (2012)
========================================================


### Load libraries

```{r, message=FALSE}
library(affy)
library(gplots)
library(doParallel)
registerDoParallel(cores=20)
library(quantro)
```

### Load `mycAffyData`

To install the `mycAffyData` from Github, use the `devtools` package. The `mycAffyData` contains the affyBatch created from the CEL files.
```{r, eval=FALSE}
library(devtools)
install_github("mycAffyData", username = "stephaniehicks")
```

Load the `mycAffyData` package which contains the `mycData` affyBatch object. 
```{r}
library(mycAffyData)
data(mycData)
sampleNames(protocolData(mycData)) <- sampleNames(mycData)
```


### Testing for global differences

```{r, message=FALSE, warning=FALSE}
pd <- pData(mycData)
pd$Group <- c("low-Myc", "low-Myc", "high-Myc", "high-Myc")
pd$Sample_Name <- sampleNames(mycData)
pmMat = pm(mycData)
colnames(pmMat) <- pd$Sample_Name
qFit = quantro(pmMat, groupFactor = pd$Group, B=1000)
qFit
```



# Expression (original scale) based on spikeins
```{r}
library(mycAffyData)
data(mycData)
probesetName <- featureNames(mycData) # ProbeSet names
probesName <- probeNames(mycData) # Probe names
pmMat <- pm(mycData)

# Extract the spike-in ProbeSet names (n=100)
ERCCind <- grep("ERCC", probeNames(mycData))
pmMatERCC <- pmMat[ERCCind,]
rowIDs <- match(rownames(pmMatERCC), rownames(pmMat))
```

#### Normalize with log2(e) - log2(colMeans(e[ERCCind]))
```{r, fig.height=5, fig.width=10}
pmMatAdj <- sweep(log2(pmMat), 2, colMeans(log2(pmMatERCC)), FUN="-")

par(mfrow=c(1,2))
matdensity(log2(pmMat), col = c(2,2,3,3))
legend('topright', c("low-Myc", "high-Myc"), lty = 1, col = c(2,3), lwd = 2)

matdensity(pmMatAdj, col = c(2,2,3,3))
legend('topright', c("low-Myc", "high-Myc"), lty = 1, col = c(2,3), lwd = 2)
```

