Analysis of `pickrellRNASeq`
========================================================

### Load libraries
```{r, message=FALSE}
library(Biobase)
library(biomaRt)
library(DESeq2)
library(quantro)
library(doParallel)
registerDoParallel(cores=20)
```



### Load `pickrellRNASeq`

```{r}
montpick.local <- load("data/montpick_eset.RData")
phenoData(montpick.eset) # gives information about the table
```

Create the RNA-Seq count table (ExpressionSet) and phenoDat. Subset for only YRI samples. 
```{r}
eset <- exprs(montpick.eset)
pd <- phenoData(montpick.eset)@data
pdYRI <- pd[which(pd$population == "YRI"), ]
esetYRI <- eset[,which(pd$population == "YRI")]
head(pdYRI)
```

Remove all the rows with zeros across all the samples in YRI
```{r}
keepMeID <- sapply(1:nrow(esetYRI), function(x){ any(esetYRI[x,] != 0) })
esetNoZerosYRI <- esetYRI[keepMeID,]
```

Import the eQTL rs7639979 from the Pickrell et al. (2012) paper
```{r}
eQTL_YRI_rs7639979 <- read.table(file="data/eQTL_YRI_rs7639979.txt", header = TRUE)
YRIgeno <- eQTL_YRI_rs7639979[match(colnames(esetNoZerosYRI), eQTL_YRI_rs7639979$SampleID),2]
table(YRIgeno)
```

Remove the NN genotype
```{r}
pdYRI$Genotype <- YRIgeno
esetNoZerosYRI <- esetNoZerosYRI[, which(pdYRI$Genotype != "NN")]
pdYRI <- pdYRI[which(pdYRI$Genotype != "NN"), ]
pdYRI$Genotype <- factor(pdYRI$Genotype, levels = c("GG", "AG", "AA"))
```


To adjust for sequence depth, we use the `rlogTransformation()` in `DESeq2`. 
```{r, eval=FALSE}
dds <- DESeqDataSetFromMatrix(countData = esetNoZerosYRI, colData = pdYRI, design = ~ 1)
rldYRI <- rlogTransformation(dds)
rldYRI.mat <- as.matrix(assay(rldYRI))
```

```{r, fig.width=10}
matdensity(rldYRI.mat, col = 1 + as.integer(pdYRI$Genotype), main = "rlogTransformation")
legend('topright', c("GG", "AG", "AA"), col = 2:4, lty = 1, lwd = 3)
matboxplot(rldYRI.mat, pdYRI, main = "rlogTransformation")
legend('topright', c("GG", "AG", "AA"), col = 2:4, lty = 1, lwd = 3)
```


### Testing for global differences

```{r}
qFit <- quantro(rldYRI.mat, groupFactor = pdYRI$Genotype, B=1000)
qFit
```




